### 2010-12-12 doc/tech_doc/a-rex/arex_tech_doc.tex
Explanation of GRID_GLOBAL_JOBID and few more words about job environment

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{projectname} -- name of the project as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{globalid} -- BES ActivityIdentifier XML tree, the global
identifier of the job
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration.
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persist if the termination of the previous 
job fails.
\item \textit{transfershare} -- name of share used in \textbf{Preparing}
and \textbf{Finishing} states.
\end{itemize}

@@

>>>>

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{projectname} -- name of the project as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{globalid} -- BES ActivityIdentifier XML tree or GridFTP URL,
 the global identifier of the job for accessing it from outside
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration.
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persist if the termination of the previous 
job fails.
\item \textit{transfershare} -- name of share used in \textbf{Preparing}
and \textbf{Finishing} states.
\end{itemize}

@@

\section{Job environment\label{sec:job}}

Because setup of resources represented by A-REX may vary a lot it is important to 
understand which features of execution environment to expect. A-REX ensures 
following:

\begin{list}{--}{\setlength{\labelwidth}{0.5cm}\setlength{\rightmargin}{\leftmargin}}
\item Specified executable is started with current directory set to session directory.
\item Executable is started under account which owns session directory.
\item Due to caching input files are not always writable by job's local account unless
\emph{readonly=no} URL option is specified for those files.
\item Environment variable GRID\_GLOBAL\_JOBID contains job's identifier usable for 
accessing job from outside through A-REX. Currently that is either XML of Activity
Identifier ot GridFTP URL depending on used interface.
\item Subject to requested Runtime Environments corresponding environment variables
are set and executable and data packages are made available.
\end{list}
